Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-09-26 paper/paper.tex
Reword to keep Craig happy

\begin{abstract}
    Despte being \NP-complete, modern subgraph isomorphism algorithms can operate comfortably on
    real-world graphs with thousands of vertices. However, they cannot handle arbitrary instances of
    this size. We show how to generate ``really hard'' random instances for subgraph isomorphism
    problems, which are computationally challenging with only a couple of hundred vertices. For the
    non-induced version of the problem, these instances lie on a satisfiable / unsatisfiable phase
    transition, whose location we can predict; for the induced variant, much richer behaviour is
    observed, and constrainedness gives a better measure of difficulty than does proximity to a
    phase transition. In both cases, we can use this to understand and improve variable and value
    ordering heuristics.

>>>>

\begin{abstract}
    Despite subgraph isomorphism being \NP-complete, modern algorithms can operate comfortably on
    real-world graphs with thousands of vertices. However, they cannot handle arbitrary instances of
    this size. We show how to generate ``really hard'' random instances for subgraph isomorphism
    problems, which are computationally challenging with only a couple of hundred vertices. For the
    non-induced version of the problem, these instances lie on a satisfiable / unsatisfiable phase
    transition, whose location we can predict; for the induced variant, much richer behaviour is
    observed, and constrainedness gives a better measure of difficulty than does proximity to a
    phase transition. In both cases, we can use this to understand and improve variable and value
    ordering heuristics.
